\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-06-19 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Start updating Results Section 4.2

\medskip
The test-case shown in this section demonstrates the model capability to capture crossflow in immiscible displacement in homogeneous porous media. The set of test-cases that we are going to illustrate starts with an elementary case in a homogeneous domain. The aim of this test-case is to validate the different simulation/scenarios \ie cross flow in a porous formation, evolution of fingers based on experimental Hele-Shaw work, behaviour of two-phase flow in more complicated formations and how factors like mobility ratio and heterogenities of the formations may affect the finger pattern. Figure \ref{fig:simple_case} describes the starting point of the simulations that will follow.

>>>>

\medskip
The test-case shown in this section demonstrates the model capability to capture crossflow in immiscible displacement in heterogeneous porous media. The numerical experiment is similar to the lab set up by \citet{evans_1994} and \citet{dawe_2008}

The set of test-cases that we are going to illustrate starts with an elementary case in a homogeneous domain. The aim of this test-case is to validate the different simulation/scenarios \ie cross flow in a porous formation, evolution of fingers based on experimental Hele-Shaw work, behaviour of two-phase flow in more complicated formations and how factors like mobility ratio and heterogenities of the formations may affect the finger pattern. Figure \ref{fig:simple_case} describes the starting point of the simulations that will follow.
